|

### 2022-07-08 paper/paper.Rmd
typos

\begin{figure*}[ht]
\centerline{\includegraphics[width=0.4\textwidth]{figures/view1_lda.png}
\includegraphics[width=0.4\textwidth]{figures/view1_rf.png}}
\caption{Model predictions in a centered slice defined by the projection onto bill depth vs flipper length, from an LDA and RF model. The colors are the same as used in the SPLOM, we see that Gentoo penugins are clearly separated, while the other two species are overlapping, and we can see the distinugishing features of the two models in terms of the different boundaries.}
\label{view1}
\end{figure*}

@@

## Shiftinh the slice center

>>>>

\begin{figure*}[ht]
\centerline{\includegraphics[width=0.4\textwidth]{figures/view1_lda.png}
\includegraphics[width=0.4\textwidth]{figures/view1_rf.png}}
\caption{Model predictions in a centered slice defined by the projection onto bill depth vs flipper length, from an LDA and RF model. The colors are the same as used in the SPLOM, we see that Gentoo penugins are clearly separated, while the other two species are overlapping, and we can see the distinguishing features of the two models in terms of the different boundaries.}
\label{view1}
\end{figure*}

@@

## Shifting the slice center
